### 2014-02-21 paper/retrofit.tex
fix step

\begin{mathpar}
\inferrule[I-step]
{|
conf tS (te) -> conf tS' te'
|}
{|
iconf iS (lconf id il tS (iniE te), ldots)
.->
iconf iS (lconf id il tS' (iniE te'), ldots)
|}

>>>>

\begin{mathpar}
\inferrule[I-step]
{|
conf tS (te) -> conf tS' te'
|}
{|
iconf iS (lconf id il tS (iniE (IT te)), ldots)
.->
iconf iS (lconf id il tS' (iniE (IT te')), ldots)
|}
